\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.65in]{geometry}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{microtype}
\usepackage{fontawesome5}

\definecolor{ink}{HTML}{000000}
\definecolor{muted}{HTML}{000000}
\definecolor{accent}{HTML}{9AA4B2}
\definecolor{accentdark}{HTML}{000000}
\definecolor{accentlight}{HTML}{FFFFFF}
\definecolor{paper}{HTML}{FFFFFF}
\definecolor{rule}{HTML}{E5E7EB}

\renewcommand{\familydefault}{\sfdefault}

\hypersetup{
  colorlinks=true,
  urlcolor=ink,
  linkcolor=ink
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=1.2em,itemsep=2pt,topsep=2pt,parsep=0pt}
\renewcommand{\arraystretch}{1.08}

\titleformat{\section}
  {\large\bfseries\color{ink}}
  {}
  {0pt}
  {\color{ink}\MakeUppercase}
\titlespacing*{\section}{0pt}{14pt}{7pt}

\newcommand{\datebadge}[1]{%
  \begingroup
  \textcolor{muted}{\footnotesize\bfseries #1}%
  \endgroup
}

\newcommand{\pill}[1]{%
  \begingroup
  \textcolor{accentdark}{\footnotesize\bfseries #1}%
  \endgroup
}

\newcommand{\cvitem}[4]{%
  \vspace{2pt}
  \begin{tabularx}{\textwidth}{@{}>{\RaggedRight\arraybackslash}X>{\RaggedLeft\arraybackslash}p{0.23\textwidth}@{}}
    \textbf{\color{ink}#1} & \datebadge{#2} \\
    {\small\color{muted}#3} & \\
  \end{tabularx}
  \vspace{-2pt}
  #4
}

\newcommand{\publication}[5]{%
  \vspace{2pt}
  \begin{tabularx}{\textwidth}{@{}>{\RaggedRight\arraybackslash}X>{\RaggedLeft\arraybackslash}p{0.18\textwidth}@{}}
    \textbf{\href{#1}{\color{ink}#2}} & \datebadge{#3}
  \end{tabularx}
  {\small #4}\par
  \vspace{1pt}
  {\small\color{muted}#5}\par
  \vspace{7pt}
}

\begin{document}

\begin{minipage}{\textwidth}
    \vspace{9pt}
    {\Huge\bfseries\color{ink} Hao Wang}\\[7pt]
    {\large\color{accentdark} Ph.D. Candidate in Computer Vision, Multimodal AI, and Agentic AI}\\
    {\color{rule}\rule{\linewidth}{0.5pt}}\\[5pt]
    \begin{tabularx}{\textwidth}{@{}X>{\RaggedLeft\arraybackslash}X@{}}
      HCP Lab, Sun Yat-sen University \& Pengcheng Laboratory &
      \faEnvelope\hspace{4pt}\href{mailto:wanghao9610@gmail.com}{wanghao9610@gmail.com} \\
      Expected graduation: December 2026 &
      \faHome\hspace{4pt}\href{https://wanghao9610.github.io/}{wanghao9610.github.io} \\
      Open to industry research roles and collaborations &
      \faPhone\hspace{4pt}+86 183 0102 8055
    \end{tabularx}
    \vspace{4pt}
\end{minipage}

\section{Profile}
Ph.D. candidate focused on open-ended visual perception, multimodal large language models, and agentic AI. My recent work builds unified models for image and video segmentation, combining language instructions, visual prompts, open-vocabulary recognition, and temporally consistent pixel-level understanding. I am particularly interested in research systems that connect foundation models with reliable pixel-level perception for practical vision applications. My future research interests will focus on the multi-modal agentic models.

\section{Education}
\cvitem
  {Sun Yat-sen University \& Pengcheng Laboratory}
  {2022.09 -- Present}
  {Ph.D. student, School of Intelligent Systems Engineering}
  {\begin{itemize}
    \item Co-supervised by Prof. Xiaodan Liang and Associate Prof. Xiangyuan Lan.
    \item Research areas: multimodal large language models, open-ended visual understanding, image/video segmentation.
    \item Expected to graduate in December 2026; actively seeking research positions in industry.
  \end{itemize}}

\cvitem
  {University of Chinese Academy of Sciences \& Institute of Automation, CAS}
  {2019.09 -- 2022.06}
  {Master student, School of Artificial Intelligence}
  {\begin{itemize}
    \item Supervised by Prof. Jing Liu.
  \end{itemize}}

\cvitem
  {Beijing Jiaotong University}
  {2015.09 -- 2019.06}
  {Bachelor student, School of Electronic and Information Engineering}
  {}

\section{Research Contributions}
  \begin{itemize}
    \item Built a line of first-author research on open-ended perception, moving from video semantic segmentation to open-vocabulary detection and multimodal any-segmentation.
    \item Developed multimodal segmentation frameworks that accept both natural-language instructions and visual prompts, aiming to bridge high-level reasoning and dense mask prediction.
    \item Explored unified image/video segmentation with memory mechanisms for temporally consistent pixel-level understanding across frames.
    \item Released project pages and code for multiple representative works, reflecting a strong preference for reproducible and open research.
  \end{itemize}

\section{Research Experience}
\cvitem
  {Meituan M17-MM}
  {2025.01 -- Present}
  {Research Intern}
  {\begin{itemize}
    \item Worked with Limeng Qiao, Lin Ma, and Guanglu Wan on multimodal segmentation and pixel-level perception.
    \item Developed X2SAM, a unified any-segmentation MLLM for images and videos with conversational instructions and visual prompts.
    \item Investigated mask memory for preserving object-level consistency in video segmentation and interactive perception.
  \end{itemize}}

\cvitem
  {Meituan Vision Intelligence Department}
  {2022.07 -- 2025.01}
  {Research Intern}
  {\begin{itemize}
    \item Worked with Zequn Jie and Lin Ma on open-vocabulary detection and multimodal segmentation systems.
    \item Contributed to OV-DINO and X-SAM, advancing open-vocabulary recognition and promptable segmentation.
    \item Studied language-aware fusion and multimodal supervision for scalable visual recognition and segmentation.
  \end{itemize}}

\cvitem
  {Tencent AI Platform Department}
  {2021.05 -- 2021.08}
  {Application Research Intern}
  {\begin{itemize}
    \item Conducted applied research in AI platform scenarios.
  \end{itemize}}

\cvitem
  {Huawei Photo Processing Department}
  {2019.09 -- 2020.07}
  {Application Project Intern}
  {\begin{itemize}
    \item Worked on applied computer vision projects for photo processing.
  \end{itemize}}

\section{First-Author Publications}
\publication
  {https://wanghao9610.github.io/X2SAM/}
  {X2SAM: Any Segmentation in Images and Videos}
  {arXiv, 2026}
  {\textbf{Hao Wang}, Limeng Qiao, Chi Zhang, Guanglu Wan, Lin Ma, Xiangyuan Lan, Xiaodan Liang}
  {Unified segmentation MLLM for images and videos, supporting conversational instructions, visual prompts, and temporally consistent mask memory. Extends any-segmentation from static images to videos while preserving dense pixel-level responses. \href{https://arxiv.org/abs/2605.00891}{Paper} \textbar{} \href{https://github.com/wanghao9610/X2SAM}{Code}}

\publication
  {https://wanghao9610.github.io/X-SAM/}
  {X-SAM: From Segment Anything to Any Segmentation}
  {AAAI, 2026}
  {\textbf{Hao Wang}, Limeng Qiao, Zequn Jie, Zhijian Huang, Chengjian Feng, Qingfang Zheng, Lin Ma, Xiangyuan Lan, Xiaodan Liang}
  {Unified MLLM framework extending segment-anything capabilities to any segmentation and pixel-level perceptual understanding. Supports flexible segmentation through multimodal inputs and instruction-driven interaction. \href{https://arxiv.org/abs/2508.04655}{Paper} \textbar{} \href{https://github.com/wanghao9610/X-SAM}{Code}}

\publication
  {https://wanghao9610.github.io/OV-DINO/}
  {OV-DINO: Unified Open-Vocabulary Detection with Language-Aware Selective Fusion}
  {arXiv, 2024}
  {\textbf{Hao Wang}, Pengzhen Ren, Zequn Jie, Xiao Dong, Chengjian Feng, Yinlong Qian, Lin Ma, Dongmei Jiang, Yaowei Wang, Xiangyuan Lan, Xiaodan Liang}
  {Unified open-vocabulary detector pre-trained on diverse large-scale datasets with language-aware selective fusion. Designed to improve category generalization by aligning visual detection with language semantics. \href{https://arxiv.org/abs/2407.07844}{Paper} \textbar{} \href{https://github.com/wanghao9610/OV-DINO}{Code}}

\publication
  {https://wanghao9610.github.io/TMANet/}
  {TMANet: Temporal Memory Attention for Video Semantic Segmentation}
  {ICIP, 2021}
  {\textbf{Hao Wang}, Weining Wang, Jing Liu}
  {Temporal memory attention for long-range video semantic segmentation without optical-flow prediction. \href{https://arxiv.org/abs/2102.08643}{Paper} \textbar{} \href{https://github.com/wanghao9610/TMANet}{Code}}

\section{Additional Publication}
\publication
  {https://ieeexplore.ieee.org/abstract/document/10096063}
  {WL-MSR: Watch and Listen for Multimodal Subtitle Recognition}
  {ICASSP, 2023}
  {Jiawei Liu, \textbf{Hao Wang}, Weining Wang, Xingjian He, Jing Liu}
  {Transformer-based multimodal subtitle recognition using OCR and ASR information with mask/crop strategies and multi-level identity embeddings.}

\section{Professional Service}
\begin{tabular}{@{}>{\bfseries}l@{\hspace{0.12\textwidth}}l@{}}
Conference Reviewer & AAAI 2026, ICCV 2023, ECCV 2024 \\
Journal Reviewer & Proceedings of the IEEE
\end{tabular}

\section{Awards}
\begin{tabular}{@{}>{\bfseries}l@{\hspace{0.13\textwidth}}l@{}}
2021.09 & 1st place in the 1st VSPW Challenge Workshop, ICCV 2021.
\end{tabular}

\end{document}
